Weakly Nonlinear MRI: Notes

### 2014-10-21 notes/mri_notes.tex
resolution of asymmetry issue and derivation of all additional hMRI terms

We can now inspect Equation \ref{momeq_added} and see that the $\hat{y}$ component of the momentum equation will pick up a term analogous to the the first term of Equation \ref{induc_eq_added} -- a tantalizing $\partial_z$ term, which has the ability to lend a $\partial_Z$ term in the $\mathcal{O}\left(\epsilon^2\right)$ equation! But Equation \ref{momeq_added} can no longer be written in terms of flux/stream functions, because contributions to the $\hat{x}$ and $\hat{z}$ components are uneven. Should I rewrite all the equations in terms of primitive variables to proceed?

>>>>

%We can now inspect Equation \ref{momeq_added} and see that the $\hat{y}$ component of the momentum equation will pick up a term analogous to the the first term of Equation \ref{induc_eq_added} -- a tantalizing $\partial_z$ term, which has the ability to lend a $\partial_Z$ term in the $\mathcal{O}\left(\epsilon^2\right)$ equation! But Equation \ref{momeq_added} can no longer be written in terms of flux/stream functions, because contributions to the $\hat{x}$ and $\hat{z}$ components are uneven. Should I rewrite all the equations in terms of primitive variables to proceed?

For the momentum equation, we now take $\partial_z$ of the x component and $\partial_x$ of the z component, to obtain, for each component:

\beq
[x]: \xi B_0 \frac{x_0}{x^2} \partial_z B_{1y} - \partial_x\partial_z B_{1y} \xi B_0 \frac{x_0}{x}
\eeq

\beq
[y]: - \xi B_0 \frac{x_0}{x^2} B_{1x}
\eeq

\beq
[z]: \xi B_0 \frac{x_0}{x^2} \partial_z B_{1y} - \partial_x\partial_z B_{1y} \xi B_0 \frac{x_0}{x}
\eeq

Rewritten in terms of flux functions:

\beq
[x]: \xi B_0 \frac{x_0}{x^2} \partial_z B_{y} - \partial_x\partial_z B_{y} \xi B_0 \frac{x_0}{x}
\eeq

\beq
[y]: - \xi B_0 \frac{x_0}{x^2} \partial_z A
\eeq

\beq
[z]: \xi B_0 \frac{x_0}{x^2} \partial_z B_{y} - \partial_x\partial_z B_{y} \xi B_0 \frac{x_0}{x}
\eeq

This means that the total added contributions to the final equation set, in $\left[\Psi, u_y, A, B_y\right]^T$ order, are:

\beq
[\Psi]: \xi B_0 \frac{x_0}{x^2} \partial_z B_{y} - \xi B_0 \partial_x\partial_z B_{y} \frac{x_0}{x}
\eeq

\beq
[u_y]: - \xi B_0 \frac{x_0}{x^2} \partial_z A
\eeq

\beq
[A]: 0
\eeq

\beq
[B]: \xi B_0 \frac{x_1}{x^2} \partial_z \Psi + \frac{1}{\reym} \xi B_0 \frac{2 x_1}{x^3}
\eeq

Two exciting things are happening. We have some first-order $\partial_z$ terms, and some linear coupling between the velocity and magnetic field equations.
